---
title: "Predictive Model For Determining Fitness Exercise Correctness"
author: "Bui Dinh Ngoc"
date: "February 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



###  Predictive Model For Determining Fitness Exercise Correctness

## Introduction

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

In this reasearch, I build a predictive model to determine whether a particular form of exercise (barbell lifting) is performed correctly. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

## Getting Data 

The dataset from [1] can be downloaded as follows:

```{r cache=T}
if (! file.exists('pml-training.csv')) {
    download.file('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv',destfile = 'pml-training.csv')
}
if (! file.exists('pml-testing.csv')) {
    download.file('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv',destfile = 'pml-testing.csv')
}

pmltraining <- read.csv('pml-training.csv')
pmltesting <- read.csv('pml-testing.csv')


```

## Cleaning Data

Only choose some useful data :

```{r}
cols <- c('roll_belt', 'pitch_belt', 'yaw_belt', 'total_accel_belt',
                  'gyros_belt_x', 'gyros_belt_y', 'gyros_belt_z',
                  'accel_belt_x', 'accel_belt_y', 'accel_belt_z',
                  'magnet_belt_x', 'magnet_belt_y', 'magnet_belt_z',
                  'roll_arm', 'pitch_arm', 'yaw_arm', 'total_accel_arm',
                  'gyros_arm_x', 'gyros_arm_y', 'gyros_arm_z',
                  'accel_arm_x', 'accel_arm_y', 'accel_arm_z',
                  'magnet_arm_x', 'magnet_arm_y', 'magnet_arm_z',
                  'roll_dumbbell', 'pitch_dumbbell', 'yaw_dumbbell', 'total_accel_dumbbell',
                  'gyros_dumbbell_x', 'gyros_dumbbell_y', 'gyros_dumbbell_z',
                  'accel_dumbbell_x', 'accel_dumbbell_y', 'accel_dumbbell_z',
                  'magnet_dumbbell_x', 'magnet_dumbbell_y', 'magnet_dumbbell_z',
                  'roll_forearm', 'pitch_forearm', 'yaw_forearm', 'total_accel_forearm',
                  'gyros_forearm_x', 'gyros_forearm_y', 'gyros_forearm_z',
                  'accel_forearm_x', 'accel_forearm_y', 'accel_forearm_z',
                  'magnet_forearm_x', 'magnet_forearm_y', 'magnet_forearm_z'
                  )
pmltesting <- pmltesting[, cols]
cols <- c(cols, 'classe')
pmltraining <- pmltraining[, cols]
```

## Predictive Model
```{r}
library(randomForest)
library(caret)

set.seed(1984)
model <- randomForest(classe ~ ., data = pmltraining, ntree=2000, importance = T)
imp = data.frame(model$importance)
features = order(-imp$MeanDecreaseGini)
inImp = createDataPartition(pmltraining$classe, p = 0.05, list = F)
featurePlot(pmltraining[inImp,features[1:4]],pmltraining$classe[inImp], plot = "pairs")
predict(model, pmltesting)

```
###
```{r}
importanceOnlyModel <- randomForest(classe ~ pitch_belt+yaw_belt+total_accel_belt+gyros_belt_x, data = pmltraining, ntree=2000, importance = T)

predict(importanceOnlyModel, pmltesting)
```
## Conclusion

If don't know the data is nonlinear or not .The best way is use the random forest to discover the most important features. Predictive model with with only importance features get 85% accuracy .
